\documentclass{academicThemeCV}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\obj}{\it Objective: Apply for pre-doctoral research assistants at top universities in the U.S.
   by \textbf{specifying} the Ph.D.-level core knowledge in economics and management, solid quantitative and coding skills,
   and various research experiences to substantiate my research potential.
   } % course-used

\begin{document}

%---------- HEADING ----------
%\vspace{-2.3cm}
\begin{center}
  \textbf{\Huge \scshape Jesse Yu-Chieh Kuo} \\ \vspace{3pt}
    %\small
  \normalsize
   %\hspace{.5pt} 
   %\href{tel:886917061223}{+886-917061223}
    %$\,|\,$ 
   \href{mailto:ujkuo@ntu.im}{ujkuo@ntu.im}
    $\,|\,$
   \textbf{\href{https://ujkuo.github.io}{https://ujkuo.github.io}} \\ \vspace{2pt}
   %{\small \obj}
   \end{center}

%----------- EDUCATION -----------

\vspace{-1em} %% course-used
\section{Education}
  \vspace{1pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {National Taiwan University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Taipei, Taiwan}
      {B.B.A.\@ in Information Management;   \textbf{GPA: 3.93} Magna cum laude}
      {Sep.\@ 2018 \textbf{-} Jun.\@ 2023} \\ 
%      \vspace{5pt}
%      \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
%        \textit{\small M.A.\@ in Economics} &
%        \textit{\small Sep.\@ 2023 \textbf{-} Exp.\@ Jun.\@ 2024}\\
%      \end{tabular*}\vspace{-7pt}
      \resumeItemListStart
        \resumeItem{\textbf{Ph.D.-level Economics Courses:}
                Microeconomics, Econometrics ({\tt Python, Stata}),
                Bayesian and Network Econometrics,
                Computational Methods for Econometrics ({\tt Python, R, Stata}),
                Economic Analysis of Social Networks ({\tt Python, R}).
                }
        \resumeItem{\textbf{Ph.D.-level Business Courses:}
                Game-Theoretic Approach Marketing,
                Information Economics, Platform Strategy.}
        \resumeItem{\textbf{Computer Science Courses:}
            Text Mining (Ph.D.-level; {\tt Python}),
            Machine Learning (Ph.D.-level; {\tt Python}),
                Data Structure and Advanced Programming ({\tt C++, Python}),
                The Design and Analysis of Algorithms ({\tt C++, Python}),
                Database ({\tt SQL}).}
        \resumeItem{\textbf{Mathematics Courses:}
                Analysis,
                % Statistics (Python),
                Advanced Statistics (Ph.D.-level),
                ODE/PDE,
                Operations Research ({\tt Python}),
                Convex Optimization (Ph.D.-level; {\tt Python}),
                Machine Learning Theory (Ph.D.-level).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  %\vspace{1pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Behavior and Data Science Research Center, National Taiwan University}{}
      {Research Assistant to
      \prof{https://sites.google.com/site/chihshenghsieh/}{Chih-Sheng Hsieh}}
%  and \textbf{\href{https://sites.google.com/view/cyruschu}{C.Y. Cyrus Chu}}}
  {Jun.\@ 2022 \textbf{-} Present}
        \resumeItemListStart
          %\resumeItem {Organized over 500 suspicious celebrities 
          %  related to the MeToo movement
          %  and assorted suspects' characteristics.}
%        \resumeItem{Collected, extracted and cleaned    
%            search records from Google Trends
%            to build complete two-year panel data.}
%        \resumeItem {Used a statistical estimation model to calibrate
%        the normalized raw search records for over 500 suspicious celebrities cleaned and extracted 
%        from Google Trends to build complete two-year panel data
%            to initiate further analysis.}
%        \resumeItem {Developed and implemented regressions to 
%          analyze the effect of big events and 
%            spillover in the MeToo movement.}
        \resumeItem {Implemented regressions to analyze the effect of big events 
        and spillover in the MeToo movement after adopting West (2021) 
        to calibrate the normalized Google Trends time-series data and build a complete two-year
        panel dataset.}
        \resumeItem {Employed the network analysis approach to examine suburbanization 
        and rural labor performance in China by using SQL to utilize a 200GB telecom
        dataset with tens of billion entries for the communication networks of mobile phones.}
        \resumeItem {Estimated the impact of users' friendship network sizes,
        behaviors, and patterns on users' selection of tariff plans, call durations,
        and cellphone models and extended to the marketing research.}
%        \resumeItem {Established and visualized large-scale networks from
%        14GB Taiwanese companies'
%            and 200GB telecom's datasets.}
        %\resumeItem {Conducted several literature reviews of corporate finance 
        %        applying social network analysis to improve further research.}
        \resumeItemListEnd
        
        \resumeSubheading
        {Department of Economics, National Taiwan University}{}
        {Research Assistant to 
        \prof{https://yu-chang-chen.github.io}{Yu-Chang Chen},
        \textbf{\href{https://sites.google.com/view/tsaihsintien/}{Hsin-Tien (Tiffany) Tsai}},
        and \textbf{\href{https://economicsatntu.wixsite.com/ming-jen-lin}{Ming-Jen Lin}},
        in \textbf{\href{https://ccl-lab.github.io}{CCL Lab}}}
        {Aug.\@ 2023 \textbf{-} Present}
        \resumeItemListStart
%        \resumeItem {Conducted literature reviews in science funding and research
%        evaluations, recommendation systems, e-commerce, and platform advertising 
%        auctions to initiate and extend current projects regarding e-commerce and science funding.}
        \resumeItem {Explored user behaviors and patterns and their 
        purchasing results by using data from a large e-commerce platform.}
        \resumeItem {Worked on extending Jeziorski and Segal (2015) to estimate consumer impatience
        in various markets using our dataset.}
        \resumeItem {Proposed research plans to evaluate and improve the usage and efficiency of research
        funds by the government.}
        \resumeItemListEnd

    \resumeSubheading
      {Department of Information Management, National Taiwan University}{}
      {Research Assistant to
      \prof{https://management.ntu.edu.tw/en/IM/faculty/teacher/sn/15}{Chih-Ping Wei}}
      {Jun.\@ 2022 \textbf{-} Feb.\@ 2023}
        \resumeItemListStart
        \resumeItem {Conducted literature reviews in economics, management, marketing,
            and finance applying sentiment analysis.}
            \resumeItem {Worked on modeling the confidence level of information from 
            online reviews toward varying sentiment and arousal.}
        \resumeItemListEnd 
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Independent Research}
  \vspace{1pt}
  \resumeSubHeadingListStart
    
%    \resumeSubheading
%    {Online Learning Behavior, Peer Effects, and Education}{}
%    {Term Project for Economics Analysis of Social Networks}{Spring 2022}
%    \resumeItemListStart
%    \resumeItem{Proposed an interdiscinpling research project
%    combining economics, computer science, education and learning science and
%    aiming at
%    uncovering the relationship between
%    the offline peer effects and online learning behavior.}
%        \resumeItem {Surveyed 40+ pieces of literatures from 
%        different fields to establish
%            the research objectives, impacts, and methodologies.}
%        \resumeItem {Sought the collaboration positively with NTU COOL, 
%            an online platform providing professors and students 
%            at National Taiwan University to hold courses and learn online,
%            to obtain large-scale online student learning behavior data.}
%    \resumeItemListEnd

  \vspace{-5pt}\item
    \textbf{Political Sentiment Analysis: 
  A Survey of U.S.\@ Media's Attitude toward China Before and After
  the Presidential Election}\\
      \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textit{\small Term Project for Text Mining} &
        \textit{\small Fall 2021}\\
      \end{tabular*}\vspace{-7pt}
    \resumeItemListStart
      \resumeItem {Employed sentimental analysis and natural language processing to 
        investigate the media's attitude
      before and after the presidential election in the U.S.\@ 
          and incorporated accessible data sources and APIs.}
     \resumeItem {Polished pre-collected 6000+ Twitter data and examined
     the text's cosine similarity with TF-IDF
          and word embedding.}
      \resumeItem {Experimented with the performance of different 
          natural language analysis and sentiment analysis packages and methods,
       then verified the sentiment change of medias and found the 
      semantic differences between pre-/post-election articles.}
    \resumeItemListEnd

    \resumeSubheading
    {Online-Offline Retailing Cooperation with BOPS Scheme under Price Competition}{}
    {Term Project for Information Economics}{Spring 2021}
    \resumeItemListStart

      \resumeItem {Surveyed tens of marketing literature related to the topics of cooperation 
      and competition between online and offline retailers
            and their relationships, especially the adoption of the BOPS 
            (Buy Online and Pick up in-Store) strategy.}
      \resumeItem {Formulated a game-theoretic model to analyze the cooperation relationship
                between online and offline retailers.}
      \resumeItem {Discussed the firm's efficiency and incentive compatibility to
              derive the conditions for successful cooperation.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \vspace{-5pt}
    \small{\item{
        \textbf{Programming: }{Python, SQL, Stata, R, Julia, shell scripts,
        C++, Git/Github, Markdown, \LaTeX.} \\[3pt]
        \textbf{Python Package: }{
        NumPy, pandas, cuDF, Matplotlib, seaborn, 
        TensorFlow, PyTorch, NLTK, scikit-learn, SciPy, statsmodels,
        BERT, pytrends, Requests, beautifulsoup4, CVXPY, RegEx, 
        Gurobi, NetworkX, geopy, Folium, PyBLP.} \\[3pt]
      %\textbf{Languages: }{Mandarin (Native), Taiwanese (Native), English (Fluent).}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
