\documentclass{smoothThemeCV}
%-------------------------------------------

% Header
\newlength{\hvspace}
\setlength{\hvspace}{-7pt}


\begin{document}

\begin{center}
    \noindent\textbf{\LARGE Jesse Yu-Chieh Kuo} \\
\end{center}
\vspace{\hvspace}
\hline
\vspace{\hvspace}
\begin{center}
    \noindent Booth School of Business \textbullet\ 5807 S. Woodlawn Ave \textbullet\ Chicago, IL 60637 \\
    \noindent\faEnvelopeO\enskip \href{mailto:ujkuo@ntu.im}{ujkuo@ntu.im}\enskip
    \faTwitter\enskip\href{https://twitter.com/ycJesseKuo}{@ycJesseKuo}\enskip
    \faGlobe\enskip\href{https://ujkuo.github.io}{ujkuo.github.io}\enskip
    |\enskip \textit{Updated: \today} \\
\end{center}
\vspace{\hvspace}
\hline
\vspace{-10pt}

% Current Position
\section*{Current Position}
\resumeSubHeadingListStart

\resumeSubheading
{The University of Chicago Booth School of Business}{Chicago, Illinois}
{Research Professional to \prof{https://sites.google.com/chicagobooth.edu/rimmyetomy/}{Rimmy E.\@ Tomy}}
{Jul.\@ 2024 \textbf{-} Present} 

\resumeSubHeadingListEnd

% Education 
\section*{Education}
\resumeSubHeadingListStart

\resumeSubheading
{The University of Chicago Booth School of Business}{Chicago, Illinois}
{Research Professional to \prof{https://sites.google.com/chicagobooth.edu/rimmyetomy/}{Rimmy E.\@ Tomy}}
{Jul.\@ 2024 \textbf{-} Present} 

\resumeSubheading
{National Taiwan University
                % \normalfont{(Admission rate: 0.09\%)}
}{Taipei, Taiwan}
{B.B.A.\@ in Information Management;   \textbf{GPA: 3.93} Magna cum laude}
{Sep.\@ 2018 \textbf{-} Jun.\@ 2023}  
                            %      \vspace{5pt}
                            %      \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
                            %        \textit{\small M.A.\@ in Economics} &
                            %        \textit{\small Sep.\@ 2023 \textbf{-} Exp.\@ Jun.\@ 2024}\\
                            %      \end{tabular*}\vspace{-7pt}
\resumeItemListStart
\resumeItem{\textbf{Ph.D.-level Economics Courses:}
    Microeconomics, Econometrics,
    Bayesian and Network Econometrics,
    Computational Methods for Econometrics,
    Economic Analysis of Social Networks.
}
\resumeItem{\textbf{Ph.D.-level Business Courses:}
    Game-Theoretic Approach Marketing,
    Information Economics, Platform Strategy.}
\resumeItem{\textbf{Computer Science Courses:}
    Text Mining (Ph.D.-level),
    Machine Learning (Ph.D.-level),
    Data Structure and Advanced Programming,
    The Design and Analysis of Algorithms,
    Database.}
\resumeItem{\textbf{Mathematics Courses:}
    Analysis,
    Advanced Statistics (Ph.D.-level),
    ODE/PDE,
    Operations Research,
    Convex Optimization (Ph.D.-level),
Machine Learning Theory (Ph.D.-level).}
\resumeItemListEnd
\resumeSubHeadingListEnd


\section*{Research}
\resumeSubHeadingListStart

\resumeSubheading
{Behavior and Data Science Research Center, National Taiwan University}{}
{Research Assistant to
\prof{https://sites.google.com/site/chihshenghsieh/}{Chih-Sheng Hsieh}}
                        %  and \textbf{\href{https://sites.google.com/view/cyruschu}{C.Y. Cyrus Chu}}}
{Jun.\@ 2022 \textbf{-} Present}
\resumeItemListStart
                                            %\resumeItem {Organized over 500 suspicious celebrities 
                                        %  related to the MeToo movement
                                        %  and assorted suspects' characteristics.}
                                  %        \resumeItem{Collected, extracted and cleaned    
                              %            search records from Google Trends
                              %            to build complete two-year panel data.}
                                  %        \resumeItem {Used a statistical estimation model to calibrate
                              %        the normalized raw search records for over 500 suspicious celebrities cleaned and extracted 
                              %        from Google Trends to build complete two-year panel data
                              %            to initiate further analysis.}
                                  %        \resumeItem {Developed and implemented regressions to 
                              %          analyze the effect of big events and 
                              %            spillover in the MeToo movement.}
\resumeItem {Implemented regressions to analyze the effect of big events 
    and spillover in the MeToo movement after adopting West (2021) 
    to calibrate the normalized Google Trends time-series data and build a 
complete two-year panel dataset.}
\resumeItem {Employed the network analysis approach to examine suburbanization 
    and rural labor performance in China by using SQL to utilize a 200GB telecom
dataset with tens of billion entries for the communication networks of mobile phones.}
\resumeItem {Estimated the impact of users' friendship network sizes,
    behaviors, and patterns on users' selection of tariff plans, call durations,
and cellphone models and extended to the marketing research.}
                                                                                                  %        \resumeItem {Established and visualized large-scale networks from
                                                                                              %        14GB Taiwanese companies'
                                                                                              %            and 200GB telecom's datasets.}
                                                                                                          %\resumeItem {Conducted several literature reviews of corporate finance 
                                                                                                      %        applying social network analysis to improve further research.}
\resumeItemListEnd

\resumeSubheading
{Department of Economics, National Taiwan University}{}
{Research Assistant to 
    \prof{https://yu-chang-chen.github.io}{Yu-Chang Chen},
    \textbf{\href{https://sites.google.com/view/tsaihsintien/}{Hsin-Tien (Tiffany) Tsai}},
    and \textbf{\href{https://economicsatntu.wixsite.com/ming-jen-lin}{Ming-Jen Lin}},
in \textbf{\href{https://ccl-lab.github.io}{CCL Lab}}}
{Aug.\@ 2023 \textbf{-} Present}
\resumeItemListStart
                                                                                                                                                                      %        \resumeItem {Conducted literature reviews in science funding and research
                                                                                                                                                                  %        evaluations, recommendation systems, e-commerce, and platform advertising 
                                                                                                                                                                  %        auctions to initiate and extend current projects regarding e-commerce and science funding.}
\resumeItem {Explored user behaviors and patterns and their 
purchasing results by using data from a large e-commerce platform.}
\resumeItem {Worked on extending Jeziorski and Segal (2015) to estimate consumer impatience
in various markets using our dataset.}
\resumeItem {Proposed research plans to evaluate and improve the usage and efficiency of research
funds by the government.}
\resumeItemListEnd

\resumeSubheading
{Department of Information Management, National Taiwan University}{}
{Research Assistant to
\prof{https://management.ntu.edu.tw/en/IM/faculty/teacher/sn/15}{Chih-Ping Wei}}
{Jun.\@ 2022 \textbf{-} Feb.\@ 2023}
\resumeItemListStart
\resumeItem {Conducted literature reviews in economics, management, marketing,
and finance applying sentiment analysis.}
\resumeItem {Worked on modeling the confidence level of information from 
online reviews toward varying sentiment and arousal.}
\resumeItemListEnd 
\resumeSubHeadingListEnd


\end{document}
