\section*{Research}
\resumeSubHeadingListStart

\resumeSubheading
{Behavior and Data Science Research Center, National Taiwan University}{}
{Research Assistant to
\prof{https://sites.google.com/site/chihshenghsieh/}{Chih-Sheng Hsieh}}
                        %  and \textbf{\href{https://sites.google.com/view/cyruschu}{C.Y. Cyrus Chu}}}
{Jun.\@ 2022 \textbf{-} Present}
\resumeItemListStart
                                            %\resumeItem {Organized over 500 suspicious celebrities 
                                                                                    %  related to the MeToo movement
                                                                                                                            %  and assorted suspects' characteristics.}
                                  %        \resumeItem{Collected, extracted and cleaned    
                                                                %            search records from Google Trends
                                                                                              %            to build complete two-year panel data.}
                                  %        \resumeItem {Used a statistical estimation model to calibrate
                                                                %        the normalized raw search records for over 500 suspicious celebrities cleaned and extracted 
                                                                                              %        from Google Trends to build complete two-year panel data
                                                                                                                            %            to initiate further analysis.}
                                  %        \resumeItem {Developed and implemented regressions to 
                                                                %          analyze the effect of big events and 
                                                                                              %            spillover in the MeToo movement.}
\resumeItem {Implemented regressions to analyze the effect of big events 
    and spillover in the MeToo movement after adopting West (2021) 
    to calibrate the normalized Google Trends time-series data and build a 
complete two-year panel dataset.}
\resumeItem {Employed the network analysis approach to examine suburbanization 
    and rural labor performance in China by using SQL to utilize a 200GB telecom
dataset with tens of billion entries for the communication networks of mobile phones.}
\resumeItem {Estimated the impact of users' friendship network sizes,
    behaviors, and patterns on users' selection of tariff plans, call durations,
and cellphone models and extended to the marketing research.}

\resumeItemListEnd

\resumeSubheading
{Department of Economics, National Taiwan University}{}
{Research Assistant to 
    \prof{https://yu-chang-chen.github.io}{Yu-Chang Chen},
    \textbf{\href{https://sites.google.com/view/tsaihsintien/}{Hsin-Tien (Tiffany) Tsai}},
    and \textbf{\href{https://economicsatntu.wixsite.com/ming-jen-lin}{Ming-Jen Lin}},
in \textbf{\href{https://ccl-lab.github.io}{CCL Lab}}}
{Aug.\@ 2023 \textbf{-} Present}
\resumeItemListStart
\resumeItem {Explored user behaviors and patterns and their 
purchasing results by using data from a large e-commerce platform.}
\resumeItem {Worked on extending Jeziorski and Segal (2015) to estimate consumer impatience
in e-commerce.}
\resumeItem {Proposed research plans to evaluate and improve the usage and efficiency of research
funds by the government.}
\resumeItemListEnd

\resumeSubheading
{Department of Information Management, National Taiwan University}{}
{Research Assistant to
\prof{https://management.ntu.edu.tw/en/IM/faculty/teacher/sn/15}{Chih-Ping Wei}}
{Jun.\@ 2022 \textbf{-} Feb.\@ 2023}
\resumeItemListStart
\resumeItem {Conducted literature reviews in economics, management, marketing,
and finance applying sentiment analysis.}
\resumeItem {Worked on modeling the confidence level of information from 
online reviews toward varying sentiment and arousal.}
\resumeItemListEnd 
\resumeSubHeadingListEnd
