%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Teaching Assistant for the course Operations Research} % Affiliation/role
    {Prof. Ling-Chieh Kung} % Organization/group
    {} % Location
    {Mar. 2022 - June. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Cooperated with 3 TAs to finish and deal with
                course-related issues.}
        \item {Detailedly examined each assignment and case study,
            and writed distinct and well-structured solutions
        with rigorous mathematical statement.} 
        \item {Wrote a course-used \LaTeX\ style file, managed
            teaching platform and solution-creating space to 
        improve the efficiency, and optimize the workflow.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Director of the department of course introduction for NTU Azalea Festival, 2021 and 2022} % Affiliation/role
    {NTUIM Student Association} % Organization/group
    {} % Location
    {Dec. 2020 - Feb. 2021, Dec. 2021 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Led a team of 5 members, assigned members to proper works and
            supervised their progress.}
        \item {Constructed the main structure of course introduction,
            surveyed plenty of courses in NTUIM and writed a majority of contents.}
        \item {Ensured the presentation is useful to high school students, 
            attemptd to deal with the information asymmetric between department 
            and high school students.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
