%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research/Teaching Experience}
\newcommand{\prof}[2]{Professor \textcolor{awesome}{\href{#1}{#2}}}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Worked with \prof{https://sites.google.com/site/chihshenghsieh/}{Chih-Sheng Hsieh}
  and \prof{https://sites.google.com/view/cyruschu}{C.Y. Cyrus Chu}}
    {Research Assistant} % Position
    {Department of Economics, NTU} % Organization
    {June 2022 - Present} % Date
    {
        \begin{cvitems}
        \item {Organized over 500 suspicious celebrities 
            related to the MeToo movement
            and collected searching records from Google Trends 
            to build a complete 2-year panal data.}
        \item {Calibrated the normalized raw data from Google Trends
            using a statistical estimation method
            to enable further analysis.}
        \item {Designed and implemented the regressions 
            to analyze the effect of certain significant events and 
            spillover effects in the MeToo movement.}
        \item {Organized a large-scale Taiwanese companies' dataset
            with millions of entries.}
        \item {Conducted literature reviews of corporate finace 
                applying social network analysis.}
        \end{cvitems}
    }
%---------------------------------------------------------

    \cventry
    {Worked with \prof{https://management.ntu.edu.tw/en/IM/faculty/teacher/sn/15}{Chih-Ping Wei}} % Prof
    {Research Assistant} % Position
    {Deparment of Information Management, NTU} % Organization
    {July 2022 - Present} % Date
    {
        \begin{cvitems}
        \item Conducted literature reviews in economics, management,
            and financial applying sentiment analysis.
        \item Organized literature in topics, data type,
            data sources, and other fields to better leverage sentimental
            analysis approachs.
        \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Worked with \prof{http://www.im.ntu.edu.tw/~lckung/}{Ling-Chieh Kung}}
    {Teaching Assistant} % Organization/group
    {Operations Research, NTU} % Location
    {March 2022 - June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Verified 3 assignments, 2 case studies, and the final exam
            and wrote 6 corresponding solutions with the rigorous mathematical
            statement and one additional
            assignment writing guidance to help and encourage students.}
        \item Built a course-oriented \LaTeX\ class file and corresponding
            document to modularize and accelerate the file 
            writing process.
        \item Graded over 300 assignments and 100 exam papers in a few days
            and managed grades for 100 enrolled students.
        \item Summarized precautions and details for the TA's work of
            this course in a handover document to help the TA in the future.
      \end{cvitems}
    }



%---------------------------------------------------------

%  \cventry
%    {Project Manager} % Job title
%    {Speech Lab, NTU} % Organization
%    {NTU, Taiwan} % Location
%    {Feb. 2019 - Dec. 2021} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Supervised by Professor Lin-Shan Lee. Organize all data for Professor Lin-Shan Lee's archive website and develop new contents.}
%        \item {Schedule progress, assign works properly to other teammates and manage task-processing.}
%        \item {Establish the work flow and optimize it by pulling in productive tools such as Notion, CI/CD, etc.}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Mentor for high school and elementary school student} % Job title
%    {Academic Tutor} % Organization
%    {Taipei, Taiwan} % Location
%    {Aug. 2018 - Present} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Taught subjects such as math, science, Chinese, article writing
%            to increase students' grades.}
%        \item {Based on students' situation to adjust teaching method. 
%                Improved the academic performance, taught students to schedule the study plan,
%              provides mock review and application documentation review.}
%        \item {As a mentor instead of a mere tutor, I also
%            \textbf{communicated with parents and students for the
%                proper education conception, 
%        resolved family conflicts and led students to explore themselves.} I believe I have a strong communication skill.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
 

%---------------------------------------------------------
\end{cventries}
