%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Course Research Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
    \cventry
    {Author}
    {Online Learning Behavior, Peer Effect, and Education}
    {Economic Analysis of Social Networks}
    {Spring 2022}
    {
        \begin{cvitems}
        \item Proposed a noval and interdiscinpling research combining economics,
            computer science, and learning science.
        \item Surveyed 40 literatures over three different fields to establish
            the research objectives, impacts, and methedologies.
        \item Sought the collaboration positively with NTU COOL, 
            an online platform providing professors and students 
            at National Taiwan University to hold courses and learn online,
            to obtain large-scale online behavior data.
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Author, Team Leader \& Presenter} % Affiliation/role
    {Modeling the Optimal Vehicle Scheduling for YouBike2.0 for NTU Campus} % Organization/group
    {Operations Research} % Location
    {Spring 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item Modeled the optimal vehicle schedule route for in-campus shared bycicles
          by linear and integer programming and graph theory.
      \item Designed the algorithm to implement the optimization problem and
          visualized the optimal routes.
      \item {Served as the project leader and assigned works and due time properly.}
      \end{cvitems}
    }

%--------------------------------------------------------
  \cventry
    {Co-Author \& Presenter}
    {Online-Offline Retailing Cooperation with BOPS Scheme under Price Competition}
    {Information Economics}
    {Spring 2021}
    {
        \begin{cvitems}
        \item Surveyed 5 papers related to the topics of coopetition between retailers,
            and online-offline relationship, especially the adoption of the BOPS 
            (Buy Oline and Pick up in-Store) strategy.
            \item Formulated a game-theoretic model to analyze the cooperation relationship
                between online and offline retailers.
            \item Discussed the firm's efficiency and incentive compatibility to
                derive the conditions for successful cooperation.
        \end{cvitems}
    }


%--------------------------------------------------------
  \cventry
  {Co-Author}
  {Political sentiment analysis based on social media:
  A survey of U.S. media's attitude toward China before and after
  the presidential election}
  {Introduction to Text Mining}
  {Fall, 2021}
  {
      \begin{cvitems}
      \item Proposed 3 research questions and directions after surveying 5 research
          papers.
      \item Studied the performance of sentence embeddings from different 
          natural language analysis and sentiment analysis packages
          to determine the package to use.
      \item Explored and compared the text's cosine similarity with TF-IDF
          and word embeddings from pre-collected 6000 tweets.
      \end{cvitems}
  }
%---------------------------------------------------------
%  \cventry
%    {Author \& Team Leader} % Affiliation/role
%    {Forecasting the components consume based on real data and providing business solutions} % Organization/group
%    {IM Freshmen Project, NTU} % Location
%    {Fall 2020} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of experience/contributions/knowledge
%        \item {The term project in the course IM Freshmen Project, 
%            advised by Professor Ling-Chieh Kung and Professor Chien-Chin Chen.}
%        \item {Implemented ML algorithms such as Linear Regression, Random Forest,
%            Gradient Boosting Regression to forecast the components consume.}
%        \item {Analyzed the company strategy and constructed business solutions
%            against problems we found in this project.}
%        \item {Assigned works properly and maintain reasonable loads to teammates,
%            optimized workflow by pulling in productive tools such as git, hackMD
%            to track everyone's contribution, and writed the report and do the presentation.}
%      \end{cvitems}
%    }
%%---------------------------------------------------------
%  \cventry
%    {Front-end Engineer} % Affiliation/role
%    {Developing an after-death-mail web-service with information-encryption based on block chain} % Organization/group
%    {IM undergraduate Project, NTU} % Location
%    {Jan. 2021 - Exp. Dec. 2021} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of experience/contributions/knowledge
%        \item {The undergraduate project for students in the NTU IM,
%            advised by Professor Chen-Chu Tsao. Co-worked with 4 teammates in the NTU IM.}
%        \item {Checked feasibility of the service, evaluated platform strategies,
%            and established potential business model.}
%        \item {Involved skills such as Javascript (espaecially React.js),
%            HTML5, CSS3 to implement the front-end of website.}
%      \end{cvitems}
%    }    

%---------------------------------------------------------
\end{cventries}
