%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
%\usepackage{fontawesome}
\usepackage[T1]{fontenc}
%\usepackage{newpxtext,newpxmath}
\usepackage{pxfonts}
\usepackage{titlesec}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[{\titlerule[1pt]}\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\prof}[2]{Professor \textbf{\href{#1}{#2}}}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-7pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    %\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-7pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.13in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Yu-Chieh Jesse Kuo} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:886917061223}{+886 917 061 223}
    $|$
    \hspace{.5pt} \href{mailto:ujkuo@ntu.im}{ujkuo@ntu.im}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/ujkuo}{github.com/ujkuo}
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{1pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {National Taiwan University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Taipei, Taiwan}
      {B.B.A. in Information Management;   \textbf{GPA: 3.98/4.30}}{September 2018 \textbf{--} June 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Ph.D. Economics Courses:}
                Microeconomic Theory, Econometrics Theory (Python, R),
                Computational Methods for Econometrics (Python, R, Stata),
                Economic Analysis of Social Networks (Python, R),
                Topics in Econometrics.}
        \resumeItem{\textbf{Ph.D. Management Courses:}
                Information Economics, Platform Strategy,
                Game-Theoretic Approach Marketing.}
        \resumeItem{\textbf{Computer Science Courses:}
            Introduction to Text Mining (Ph.D. level; Python),
            Machine Learning (Ph.D. level; Python),
                Data Structure and Advanced Programming (C++, Python),
                The Design and Analysis of Algorithms (Python),
                Database Management (SQL),
                System Analysis and Design,
                Computer Networks and Applications.}
        \resumeItem{\textbf{Mathematics Courses:}
                Calculus,
                Statistics,
                Advanced Statistics (Ph.D. level),
                ODE/PDE,
                Linear Algebra,
                Operations Research (Python),
                Convex Optimization (Ph.D. level; Python).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{1pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Department of Economics, National Taiwan University}{}
      {Research Assistant to
      \prof{https://sites.google.com/site/chihshenghsieh/}{Chih-Sheng Hsieh}
  and \prof{https://sites.google.com/view/cyruschu}{C.Y. Cyrus Chu}}
  {Jun 2022 \textbf{--} Present}
        \resumeItemListStart
          \resumeItem {Organized over 500 suspicious celebrities 
            related to the MeToo movement
            and collected suspects' characteristics and
            searching records from Google Trends 
            to build a complete 2-year panal data.}
        \resumeItem {Used a statistical estimation model to calibrate
        the normalized raw data from Google Trends
            to enable further analysis.}
        \resumeItem {Analyzed the effect of certain big events and 
            spillover effects in the MeToo movement by implementing the regressions.}
        \resumeItem {Conducted and visualized a large-scale networks from
        14GB Taiwanese companies' dataset
            with millions of entries.}
        \resumeItem {Conducted several literature reviews of corporate finace 
                applying social network analysis to improve further research.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Department of Information Management, National Taiwan University}{}
      {Research Assistant to
      \prof{https://management.ntu.edu.tw/en/IM/faculty/teacher/sn/15}{Chih-Ping Wei}}
      {June 2022 \textbf{--} Present}
        \resumeItemListStart
        \resumeItem {Conducted literature reviews in economics, management,
            and financial applying sentiment analysis.}
        \resumeItem{Organized literature in topics, data sources,
        and other fields to better leverage sentimental analysis approachs.}
        \resumeItemListEnd 
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Independent Research}
  \vspace{1pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
    {Online Learning Behavior, Peer Effects, and Education}{}
    {Term Project for Economics Analysis of Social Networks}{Spring 2022}
    \resumeItemListStart
        \resumeItem {Proposed an interdiscinpling research combining economics,
            computer science, education, and learning science.}
        \resumeItem {Surveyed 40 literatures over three different fields to establish
            the research objectives, impacts, and methedologies.}
        \resumeItem {Sought the collaboration positively with NTU COOL, 
            an online platform providing professors and students 
            at National Taiwan University to hold courses and learn online,
            to obtain large-scale online behavior data.}
    \resumeItemListEnd

  \vspace{-7pt}\item
    \textbf{Political sentiment analysis: 
  A survey of U.S. media's attitude toward China during the presidential election}\\
      \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textit{\small Term Project for Introduction to Text Mining} &
        \textit{\small Fall 2021}\\
      \end{tabular*}\vspace{-7pt}
    \resumeItemListStart
      \resumeItem {Proposed 3 research questions and directions after surveying 5
          literature regarding sentimental analysis on economics.}
      \resumeItem {Studied and compared
      the performance of sentence embeddings from different 
          natural language analysis and sentiment analysis packages and methods
          to determine the package to use.}
      \resumeItem {Explored and compared the text's cosine similarity with TF-IDF
          and word embeddings from pre-collected 6000 tweets.}
    \resumeItemListEnd

    \resumeSubheading
    {Online-Offline Retailing Cooperation with BOPS Scheme under Price Competition}{}
    {Term Project for Information Economics}{Spring 2021}
    \resumeItemListStart

      \resumeItem {Surveyed 5 papers related to the topics of coopetition between retailers,
            and online-offline relationship, especially the adoption of the BOPS 
            (Buy Oline and Pick up in-Store) strategy.}
      \resumeItem {Formulated a game-theoretic model to analyze the cooperation relationship
                between online and offline retailers.}
      \resumeItem {Discussed the firm's efficiency and incentive compatibility to
              derive the conditions for successful cooperation.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
%----------- SKILLS -----------

\section{Skills}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \vspace{-5pt}
    \small{\item{
        \textbf{Programming: }{Python, R, Stata, shell scripts,
        SQL, C++, Git/Github, Markdown, \LaTeX.} \\ 
        \textbf{Python Package: }{
          Numpy, Pandas, Matplotlib, Tensorflow, Torch, nltk, Sklearn, Scipy, Statsmodel,
        BERT, pytrends, cvxpy,
        gurobi, NetworkX.} \\
      \textbf{Languages: }{Chinese(Mandarin), Taiwanese, English}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
