%-------------------------
% Resume in Latex
% Author : Aras Gungore, Yu-Chieh (Jesse) Kuo
% Compiler : XeLaTeX
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
%\usepackage{fontawesome}
\usepackage[T1]{fontenc}
%\usepackage{newpxtext,newpxmath}
\usepackage{pxfonts}
\usepackage{titlesec}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[{\titlerule[1pt]}\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\prof}[2]{Professor \textbf{\href{#1}{#2}}}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-7pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    %\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-7pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.13in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge \scshape Yu-Chieh (Jesse) Kuo} \\ \vspace{3pt}
    \small
   \hspace{.5pt} \href{tel:886917061223}{+886-917-061-223}
    $|$
    \hspace{.5pt} \href{mailto:ujkuo@ntu.im}{ujkuo@ntu.im}
    $|$
   \hspace{.5pt} \textbf{\href{https://ujkuo.github.io}{Personal Page}}
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{1pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {National Taiwan University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Taipei, Taiwan}
      {B.B.A. in Information Management;   \textbf{GPA: 3.98/4.30}}{September 2018 \textbf{-} June 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Ph.D. Economics Courses:}
                Microeconomics, Econometrics (Python, R),
                Computational Methods for Econometrics (Python, R, Stata),
                Economic Analysis of Social Networks (Python, R),
                Topics in Econometrics.}
        \resumeItem{\textbf{Ph.D. Business Courses:}
                Game-Theoretic Approach Marketing,
                Information Economics, Platform Strategy.}
        \resumeItem{\textbf{Computer Science Courses:}
            Text Mining (Ph.D. level; Python),
            Machine Learning (Ph.D. level; Python),
                Data Structure and Advanced Programming (C++, Python),
                The Design and Analysis of Algorithms (Python),
                Database Management (SQL),
                System Analysis and Design,
                Computer Networks.}
        \resumeItem{\textbf{Mathematics Courses:}
                Calculus,
                Statistics (Python),
                Advanced Statistics (Ph.D. level),
                ODE/PDE,
                Linear Algebra,
                Operations Research (Python),
                Convex Optimization (Ph.D. level; Python).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{1pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Behavior and Data Science Research Center, National Taiwan University}{}
      {Research Assistant to
      \prof{https://sites.google.com/site/chihshenghsieh/}{Chih-Sheng Hsieh}
  and \prof{https://sites.google.com/view/cyruschu}{C.Y. Cyrus Chu}}
  {June 2022 \textbf{-} Present}
        \resumeItemListStart
          \resumeItem {Organized over 500 suspicious celebrities 
            related to the MeToo movement
            and assorted suspects' characteristics.}
        \resumeItem{Collected, extracted and cleaned    
            search records from Google Trends
            to build complete two-year panel data.}
        \resumeItem {Used a statistical estimation model to calibrate
        the normalized raw data from Google Trends
            to enable further analysis.}
        \resumeItem {Developed and implemented programs to 
          analyzed the effect of big events and 
            spillover in the MeToo movement.}
        \resumeItem {Conducted and visualized large-scale networks from
        14GB Taiwanese companies' dataset
            with millions of entries.}
        \resumeItem {Conducted several literature reviews of corporate finance 
                applying social network analysis to improve further research.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Department of Information Management, National Taiwan University}{}
      {Research Assistant to
      \prof{https://management.ntu.edu.tw/en/IM/faculty/teacher/sn/15}{Chih-Ping Wei}}
      {June 2022 \textbf{-} Present}
        \resumeItemListStart
        \resumeItem {Conducted literature reviews in economics, business, marketing,
            and finance applying sentiment analysis.}
            \resumeItem {Worked on modeling the confidence level of information from 
            online reviews toward varying sentiment and arousal.}
        \resumeItemListEnd 
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Independent Research}
  \vspace{1pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
    {Online Learning Behavior, Peer Effects, and Education}{}
    {Term Project for Economics Analysis of Social Networks}{Spring 2022}
    \resumeItemListStart
    \resumeItem{Proposed an interdiscinpling research project
    combining economics, computer science, education and learning science and
    aiming at
    uncovering the relationship between
    the offline peer effects and online learning behavior.}
        \resumeItem {Surveyed 40 pieces of literatures from 
        different fields to establish
            the research objectives, impacts, and methodologies.}
        \resumeItem {Sought the collaboration positively with NTU COOL, 
            an online platform providing professors and students 
            at National Taiwan University to hold courses and learn online,
            to obtain large-scale online student learning behavior data.}
    \resumeItemListEnd

  \vspace{-7pt}\item
    \textbf{Political Sentiment Analysis: 
  A Survey of U.S. Media's Attitude toward China Before and After
  the Presidential Election}\\
      \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textit{\small Term Project for Text Mining} &
        \textit{\small Fall 2021}\\
      \end{tabular*}\vspace{-7pt}
    \resumeItemListStart
      \resumeItem {Proposed the main research topic for discussing the media's attitude
      before and after the election after surveying five pieces of 
          literature regarding sentimental analysis of economics
          and found different accessible data resources.}
      \resumeItem {Studied and compared
      the performance of sentence embeddings from different 
          natural language analysis and sentiment analysis packages and methods
          to determine the package to use and checked the scrapped data quality.}
      \resumeItem {Explored and compared the text's cosine similarity with TF-IDF
          and word embeddings from pre-collected 6000 tweets.}
    \resumeItemListEnd

    \resumeSubheading
    {Online-Offline Retailing Cooperation with BOPS Scheme under Price Competition}{}
    {Term Project for Information Economics}{Spring 2021}
    \resumeItemListStart

      \resumeItem {Surveyed five pieces of literature related to the topics of competition between retailers
            and online-offline relationships, especially the adoption of the BOPS 
            (Buy Online and Pick up in-Store) strategy.}
      \resumeItem {Formulated a game-theoretic model to analyze the cooperation relationship
                between online and offline retailers.}
      \resumeItem {Discussed the firm's efficiency and incentive compatibility to
              derive the conditions for successful cooperation.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
%----------- SKILLS -----------

\section{Skills}
  \vspace{1pt}
  \resumeSubHeadingListStart
    \vspace{-5pt}
    \small{\item{
        \textbf{Programming: }{Python, R, Stata, shell scripts,
        SQL, C++, Git/Github, Markdown, \LaTeX.} \\ 
        \textbf{Python Package: }{
          NumPy, pandas, Matplotlib, TensorFlow, PyTorch, NLTK, scikit-learn, SciPy, statsmodels,
        BERT, pytrends, Requests, beautifulsuop4, CVXPY, RegEx, 
        Gurobi, NetworkX.} \\
      \textbf{Languages: }{Chinese(Mandarin), Taiwanese, English.}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
